Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex

%
%
%We examine the effect of the non-linear Poiseuille flow on the migration of
%semi-permeable vesicle. In this experiment, the vesicle is initialized
%above the center line $y=0$, and it migrates towards the center
%line~\cite{dan-vla-mis2009}. 
%
%For an impermeable vesicle, depending on
%the vesicles reduced area and the flow rate, the equilibrium vesicle shape
%is either an axisymmetric parachute or bullet, or an asymmetric
%tank-treading slipper~\cite{kao-bir-mis2009}. 
%We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}.
%One of the most salient features of an impermeable vesicle in the Poiseuille flow is that, 
%%
%%To validate our methods,
%%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%%for the steady state shape of an impermeable vesicle
%%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%%qualitatively agree, Kaoui et al.~report that the vesicles with
%%$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%%are undergoing a tank treading motion, and we therefore report them as
%%asymmetric slippers.
%
%Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow. 
Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
final vesicle configurations are in
Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
%
As observed for the planar shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the steady state reduced area in
Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U
= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper. We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow. The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.

>>>>

%
%
%We examine the effect of the non-linear Poiseuille flow on the migration of
%semi-permeable vesicle. In this experiment, the vesicle is initialized
%above the center line $y=0$, and it migrates towards the center
%line~\cite{dan-vla-mis2009}. 
%
%For an impermeable vesicle, depending on
%the vesicles reduced area and the flow rate, the equilibrium vesicle shape
%is either an axisymmetric parachute or bullet, or an asymmetric
%tank-treading slipper~\cite{kao-bir-mis2009}. 
%We validated our numerical codes by comparing against results in Kaoui {\it et al.} \cite{kao-bir-mis2009}.
%One of the most salient features of an impermeable vesicle in the Poiseuille flow is that, 
%%
%%To validate our methods,
%%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%%for the steady state shape of an impermeable vesicle
%%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%%qualitatively agree, Kaoui et al.~report that the vesicles with
%%$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%%are undergoing a tank treading motion, and we therefore report them as
%%asymmetric slippers.
%
%Having validated our method, we investigate the dynamics of a semi-permeable vesicle in a Poiseuille flow.

Using several initial
$U(1-(y/W)^2,0)$, where $U$ is the maximum imposed velocity. We examine
the effect of the non-linear Poiseuille flow on the migration of
semi-permeable vesicle. In this experiment, the vesicle is initialized
above the center line $y=0$, and it migrates towards the center
line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
the vesicles reduced area and the flow rate, the long time vesicle shape
is either an axisymmetric parachute or bullet, or an asymmetric
tank-treading slipper~\cite{kao-bir-mis2009}. To validate our methods,
in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
for the steady state shape of an impermeable vesicle
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The
final vesicle configurations are in
Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
%
As observed for the planar shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the steady state reduced area in
Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper. We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow. The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.
